Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)

### 2022-12-02 R/model_fcs_check.Rmd
Update FCS (image size)

---
title: "Favourable Conservation Status (FCS): <br> Analysis of Bauer et al. (unpublished) Field experiment"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: jpeg
    fig_width: 12
    fig_height: 6
---

@@

```{r collapse = TRUE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m_full
m_1$formula
m_2$formula
m_1$family
m_2$family
```

>>>>

---
title: "Analysis of Bauer et al. (unpublished) Field experiment: <br> Favourable Conservation Status (FCS)"
author: "<b>Markus Bauer*</b> <br>"
date: "<b>`r format(Sys.time(), '%Y-%m-%d')`</b>"
output:
  github_document:
    toc: true
    toc_depth: 3
    dev: jpeg
    fig_width: 7
    fig_height: 5
---

@@

```{r collapse = TRUE}
load(file = here("outputs", "models", "model_fcs_2.Rdata"))
load(file = here("outputs", "models", "model_fcs_full.Rdata"))
m_1 <- m2
m_2 <- m_full
```

```{r collapse = TRUE}
m_1$formula
m_2$formula
```

```{r collapse = TRUE}
m_1$family
m_2$family
```
